Subject-level developmental relationships

### 2024-08-29 3_developmental_relationships.qmd

```{r, fig.width=9, fig.height=9}
GGally::ggpairs(select(d_sub_cdi, log_age, rt,  
                       long_window_accuracy, prod, comp), 
        progress = FALSE, lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

@@

>>>>

```{r, fig.width=9, fig.height=9}
GGally::ggpairs(select(d_sub_cdi, log_age, rt,  
                       long_window_accuracy, short_window_accuracy, prod, comp), 
        progress = FALSE, lower = list(continuous = GGally::wrap("points", alpha = 0.03)))

@@

Make into matrices.

@@

d_sub_cdi_mat <- d_sub_cdi_mat |>
  filter(complete.cases(d_sub_cdi_mat)) |>
  as.matrix() 
```

Factor analysis

```{r}
# scree(d_sub_cdi_mat, pc=FALSE)  # Use pc=FALSE for factor analysis

# install.packages("psych")
mod1 <- fa(d_sub_cdi_mat, 1)
mod2 <- fa(d_sub_cdi_mat, 2)

```{r}
